# Visit dates {#visit}

Source: https://epi-wiki.erasmusmc.nl/wiki/ergowiki/index.php/Response_data

1. Import data for all cohorts

```{r, eval = FALSE}
rs1_1 <- read_sav(here::here("00_raw_data", "visits", "Ergo1ResponseDetail_(22-jan-2015)_excerpt.sav"))
rs1_2 <- read_sav(here::here("00_raw_data", "visits", "Ergo2ResponseDetail_(22-jan-2015)_excerpt.sav"))
rs1_3 <- read_sav(here::here("00_raw_data", "visits", "e3_(3)_RESPONS_(22-feb-2016)_excerpt.sav"))
rs1_4 <- read_sav(here::here("00_raw_data", "visits", "e4_(4)_RESPONS_(12-mar-2018)_excerpt.sav"))
rs1_5 <- read_sav(here::here("00_raw_data", "visits", "e5_(5)_RESPONS_(22-jun-2016)_excerpt.sav"))
rs1_6 <- read_sav(here::here("00_raw_data", "visits", "e6_(6)_RESPONS_(10-feb-2017)_EXCERPT.sav"))
rs2_1 <- read_sav(here::here("00_raw_data", "visits", "ep_(1)_RESPONS_(15-jan-2019)_excerpt.sav"))
rs3_1 <- read_sav(here::here("00_raw_data", "visits", "ej_(1)_RESPONS_(04-apr-2016)_excerpt.sav"))
```

2. Split datasets:

```{r, eval = FALSE}

#1. Separate rs1_4 into rs1, rs2

rs2_2 <- rs1_4 %>%
  filter(rs_cohort == 2)

rs1_4 <- rs1_4 %>%
  filter(rs_cohort == 1)

#2. Separate rs1_5 into rs1, rs2, rs3
rs3_2 <- rs1_5 %>%
  filter(rs_cohort == 3)

rs2_3 <- rs1_5 %>%
  filter(rs_cohort == 2)

rs1_5 <- rs1_5 %>%
  filter(rs_cohort == 1)

#3. rs1_6 into rs1 and rs2 
rs2_4 <- rs1_6 %>%
  filter(rs_cohort == 2)

rs1_6 <- rs1_6 %>%
  filter(rs_cohort == 1)

```

3. Merge the data for all visits, by cohort:

```{r eval = FALSE}

### Merge RSI

rs1 <- list(rs1_1, rs1_2, rs1_3, rs1_4, rs1_5, rs1_6)

rs1_vis <- reduce(rs1, left_join, by = c("ergoid", "rs_cohort"))

### NOTE: RS1_2 had only 1 center visit and no home interview!

### Merge RS2
rs2 <- list(rs2_1, rs2_2, rs2_3, rs2_4)

rs2_vis <- reduce(rs2, left_join, by = c("ergoid", "rs_cohort"))

### Merge RS3

rs3_vis <- rs3_1  %>%
  left_join(rs3_2, by = c("ergoid", "rs_cohort"))
```

4. Select and rename the specific variables from the combined dataset, by cohort: In this case we selected the variables for the interview date.

```{r, eval = FALSE}
rs1_interview <- rs1_vis %>%
  select(ergoid, rs_cohort, e1_aintdat, e2_bcendat, e3_3493, e4_3493, e5_3493, e6_3493) %>% 
  rename(e1 = e1_aintdat, e2 = e2_bcendat, e3 = e3_3493, e4 = e4_3493, e5 = e5_3493, e6 = e6_3493)

rs2_interview <- rs2_vis %>%
  select(ergoid, rs_cohort , ep_3493, e4_3493, e5_3493, e6_3493) %>% 
  rename(e3 = ep_3493, e4 = e4_3493, e5 = e5_3493, e6 = e6_3493)
  
rs3_interview <- rs3_vis %>%
  select(ergoid, rs_cohort , ej_3493, e5_3493) %>% 
  rename(e4 = ej_3493, e5 = e5_3493)
```

5. Bind, if necessary, the cohorts. Since the variable names are consistent through the datasets.

```{r, eval = FALSE}
visits <- rs1_interview %>% 
  bind_rows(rs2_interview) %>% 
  bind_rows(rs3_interview)
```

7. Export the variable to a `clean_data` folder.

```{r, eval = FALSE}
export(visits, here::here("02_clean_data", "visits.Rdata"))
```

