# BMI, weight and height {#bmi}

Source: 

- https://epi-wiki.erasmusmc.nl/wiki/ergowiki/index.php/E1_anthropo
- https://epi-wiki.erasmusmc.nl/wiki/ergowiki/index.php/E2_anthropo
- https://epi-wiki.erasmusmc.nl/wiki/ergowiki/index.php/E5_anthropo

1. Import data for all cohorts

```{r, eval = FALSE}
bmi1_1 <- read_sav(here::here("00_raw_data", "anthro", "/e1_ANTHROPO_(15-jun-2011).sav"))
bmi1_2 <- read_sav(here::here("00_raw_data", "anthro", "/e2_(2)_ANTHROPO_(26-apr-2011).sav"))
bmi1_3 <- read_sav(here::here("00_raw_data", "anthro", "/e3_(3)_HARTVAAT_(25-feb-2013)_ANTHROPO.sav"))
bmi1_4 <- read_sav(here::here("00_raw_data", "anthro", "/e4_(4)_UITSCHR_(06-nov-2014)_ANTHROPO-PART.sav"))
bmi1_5 <- read_sav(here::here("00_raw_data", "anthro", "/e5_(5)_ANTHROPO_(10-dec-2015).sav"))
bmi1_6 <- read_sav(here::here("00_raw_data", "anthro", "/e6_(6)_ANTHROPO_(25-apr-2017).sav"))
bmi2_1 <- read_sav(here::here("00_raw_data", "anthro", "/ep_(1)_LICHONDZ_(18-oct-2012)_ANTHROPO.sav"))
bmi3_1 <- read_sav(here::here("00_raw_data", "anthro", "/ej_(1)_UITSCHR_(23-feb-2010)_ANTHROPO-PART.sav"))
```

2. Split datasets:

```{r, eval = FALSE}

# 1. Separate bmi1_4 into rs1 and rs2
bmi2_2 <- bmi1_4 %>%
  filter(rs_cohort == 2)

bmi1_4 <- bmi1_4 %>%
  filter(rs_cohort == 1)

# 2. Separate bmi1_5 into rs1, rs2, rs3
bmi3_2 <- bmi1_5 %>%
  filter(rs_cohort == 3)

bmi2_3 <- bmi1_5 %>%
  filter(rs_cohort == 2)

bmi1_5 <- bmi1_5 %>%
  filter(rs_cohort == 1)

# 3. Separate bmi1_6 into rs1 and rs2
bmi1_6 <- bmi1_6 %>%
  filter(rs_cohort ==1)

bmi2_4 <- bmi1_6 %>%
  filter(rs_cohort ==2)
```

3. Merge the data for all visits, by cohort:

```{r eval = FALSE}

# Merge cohorts for rs1

bmi1 <- list(bmi1_1, bmi1_2, bmi1_3, bmi1_4, bmi1_5, bmi1_6)

rs1_bmi <- reduce(bmi1, left_join, by = c("ergoid", "rs_cohort"))

# Merge cohorts for rs2

bmi2 <- list(bmi2_1, bmi2_2, bmi2_3, bmi2_4)

rs2_bmi <- reduce(bmi2, left_join, by = c("ergoid", "rs_cohort"))

# Merge cohorts for rs3

bmi3 <- bmi3_1 %>%
  left_join(bmi3_2, by= c("ergoid", "rs_cohort"))

```

4. Select and rename the specific variables from the combined dataset, by cohort: In this case we selected the variables for the interview date.

```{r, eval = FALSE}

rs1_bmi <- rs1_bmi%>%
  select(ergoid, rs_cohort, e1_aahgt, e1_aawgt, e2_229, 
         e2_230, e3_229, e3_230, e4_229, e4_230, e5_229, 
         e5_230,e6_229,e6_230) %>%
  rename(hgt1 = e1_aahgt, hgt2 = e2_229, hgt3 = e3_229, 
         hgt4 = e4_229, hgt5 = e5_229, hgt6 = e6_229,
         wgt1 = e1_aawgt, wgt2 = e2_230, wgt3 = e3_230, 
         wgt4 = e4_230, wgt5 = e5_230, wgt6 = e6_230)

rs2_bmi <- rs2_bmi%>%
  select(ergoid, rs_cohort, ep_229, ep_230, e4_229, 
         e4_230, e5_229, e5_230,e6_229,e6_230) %>%
  rename(hgt3 = ep_229, hgt4 = e4_229, hgt5 = e5_229, hgt6 = e6_229,
         wgt3 = ep_230, wgt4 = e4_230, wgt5 = e5_230, wgt6 = e6_230)


rs3_bmi <- bmi3%>%
  select(ergoid,  rs_cohort, ej_229, ej_230, e5_229, e5_230) %>%
  rename(hgt4 = ej_229, hgt5 = e5_229,
         wgt4 = ej_230, wgt5 = e5_230)
```

5. Bind, if necessary, the cohorts. Since the variable names are consistent through the datasets.

```{r, eval = FALSE}
rs_bmi <- rs1_bmi %>%
  bind_rows(rs2_bmi) %>%
  bind_rows(rs3_bmi)
```

6. Create `bmi` variable

```{r, eval = FALSE}
rs_bmi <- rs_bmi %>%
  mutate(bmi1 = wgt1/((hgt1/100)^2),
         bmi2 = wgt2/((hgt2/100)^2),
         bmi3 = wgt3/((hgt3/100)^2),
         bmi4 = wgt4/((hgt4/100)^2),
         bmi5 = wgt5/((hgt5/100)^2),
         bmi6 = wgt6/((hgt6/100)^2))
```

7. Export the variable to a `clean_data` folder.

```{r, eval = FALSE}
export(rs_bmi, here::here("02_clean_data", "bmi.Rdata"))
```


