# Laboratory data {#lab}


Source: https://epi-wiki.erasmusmc.nl/wiki/ergowiki/index.php/Cholesterol

We included cholesterol and hdl since they were sistematically collected across visits for all cohorts. 
*Note*: There are no laboratory data for visit RS-I-2

Glucose has the subfix: **v3846**, but since it was collected in different ways and not in all waves, we don't include it, but it could be collected using the same code.

1. Import data for all cohorts

```{r, eval = FALSE}
chol1_1 <- import(here::here("00_raw_data", "cholesterol",  "e1_CHOLESTEROL_(10.03.2010).sav"))
chol1_3 <- import(here::here("00_raw_data", "cholesterol",  "e3_(3)_LAB_(10-mar-2010).sav"))
chol1_4 <- import(here::here("00_raw_data", "cholesterol",  "e4_(4)_LAB_(10-mar-2010)b.sav"))
chol1_5 <- import(here::here("00_raw_data", "cholesterol",  "e5_(5)_LAB_(29-aug-2014)r.sav"))
chol2_1 <- import(here::here("00_raw_data", "cholesterol",  "ep_(1)_LAB_(15-mar-2010).sav"))
chol3_1 <- import(here::here("00_raw_data", "cholesterol",  "ej_(1)_LAB_(11-jun-2009)r.sav"))
```

2. Split datasets:
  
```{r, eval = FALSE}

# 1. Separate chol1_4 into rs1, rs2, rs3

chol2_2 <- chol1_4 %>%
  filter(rs_cohort == 2)

chol1_4 <- chol1_4 %>%
  filter(rs_cohort == 1)

# 2. Separate chol1_5 into rs1, rs2, rs3

chol3_2 <- chol1_5 %>%
  filter(rs_cohort == 3)

chol2_3 <- chol1_5 %>%
  filter(rs_cohort == 2)

chol1_5 <- chol1_5 %>%
  filter(rs_cohort == 1)

# 3. Separate chol1_6 into rs1 and rs2

# Not available

```

3. Merge the data for all visits, by cohort:
  
```{r, eval = FALSE}

### Merge RSI

chol1 <- list(chol1_1, chol1_3, chol1_4, chol1_5)#, chol1_6)

rs1_chol <- reduce(chol1, left_join, by = c("ergoid"))

### Merge RSII

chol2 <- list(chol2_1, chol2_2, chol2_3)#,chol2_4)

rs2_chol <- reduce(chol2, left_join, by = c("ergoid"))

### Merge RSIII

chol3 <- list(chol3_1, chol3_2)

rs3_chol <- reduce(chol3, left_join, by = c("ergoid"))

```

4. Select and rename variables:

```{r, eval = FALSE}

rs1_chol <- rs1_chol %>% 
  select(ergoid, e1_al7_chl, e1_al7_hdl, ends_with("_3845"), ends_with("_4107")) %>%
  rename(chol1 = e1_al7_chl,
         chol3 = e3_3845,
         chol4 = e3_3845,
         chol5 = e5_3845,
         hdl1 = e1_al7_hdl,
         hdl3 = e3_4107,
         hdl4 = e4_4107,
         hdl5 = e5_4107)

rs2_chol <- rs2_chol %>% 
  select(ergoid, ends_with("_3845"), ends_with("_4107")) %>%
  rename(chol3 = ep_3845,
         chol4 = e4_3845,
         chol5 = e5_3845,
         hdl3 = ep_4107,
         hdl4 = e4_4107,
         hdl5 = e5_4107)


rs3_chol <- rs3_chol %>% 
  select(ergoid, ends_with("_3845"), ends_with("_4107")) %>%
  rename(chol4 = ej_3845,
         chol5 = e5_3845,
         hdl4 = ej_4107,
         hdl5 = e5_4107)

```

5. Bind , the cohorts. Since the variable names are consistent through the datasets.

```{r, eval = FALSE}
chol <- rs1_chol %>%
  bind_rows(rs2_chol) %>%
  bind_rows(rs3_chol)
```

6. Export the variable to a `clean_data` folder.

```{r, eval = FALSE}
export(chol, here::here("02_clean_data", "chol.Rdata"))
```
